Properties of quasar microlensing light curves: probing its internal structure

### 2015-07-20 paper1/ms.tex
title and authors edited

\documentclass[usenatbib,onecolumn]{mn2e}

\usepackage{amsmath}
\usepackage{graphicx}

\title{Microlensing as a possible probe of the internal structure of quasars}

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,
\newauthor
Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

>>>>

\documentclass[usenatbib]{mn2e}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multicol}

\title[Quasar microlensing and its internal structure]{Properties of quasar microlensing light curves: probing its internal structure}
% \title{Microlensing as a possible probe of the internal structure of quasars}

\author[Tomozeiu et al]{Mihai Tomozeiu\thanks{mihai@physik.uzh.ch},$^{1,2}$ 
Irshad Mohammed,$^{1,2}$ 
Manuel Rabold,$^{1,2}$
Prasenjit Saha,$^{1,2}$  
\newauthor
and Joachim Wambsganss$^3$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Zentrum f\"ur Astronomie der Universit\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}
